Parameterization of the responses of subarctic European vegetation to key environmental variables for ozone risk assessment

### 2022-05-07 VegOzone.tex
Move conclusions
Move text to conclusions and rephrase

We estimated the biomass reductions in accordance to the CLs \citep{ICP:MappingManual2017, ESPR:Hayes2021} for the most extreme temperature parameterization localization (\emph{subarctic}) for each PFT. The estimates for SWP=off are listed in Table~\ref{tab:biomass_reduction}. We defined an uncertainty range from the difference in biomass reduction caused by the variation of $f_\mathrm{light}$. Superscript refers to PPFD0.8 and subscript to PPFD1.2. The reported range corresponds to the effect of taking SWP into account or not. As SWP reduces $\mathrm{POD_1}$, biomass reduction is decreased when taking SWP into account. The biomass reduction ranges between $2.5\,\unit{\%}$ (coniferous, 2018) and $17.4\,\unit{\%}$ (deciduous, 2019). For deciduous trees this amounts to a reduction by up to $55\,\unit{\%}$ compared to MM. From an agro-economical point of view in our focus area, where the grass is cut only once a year, a loss of biomass of more than $10\,\unit{\%}$ can have severer consequences compared to more productive areas in central Europe. Therefore, CL may also need localization.
Coniferous trees are the least affected PFT and the magnitude of total biomass reduction is almost independent of the choice of the parameterization within given uncertainties.

@@

In summary, 2018 was warmer, drier, and brighter than usual, while 2019 was a rather average year. Ozone was more enhanced in 2018 than 2019. This means that the drought conditions in summer 2018 contributed more strongly to lower $\mathrm{POD_1}$ than elevated $\chem{\chi_{O_3}}$ in our $\mathrm{DO_3SE}$ modeling results.

@@

@@

For our study, we conducted a similar bio-monitoring study at Svanhovd, a site with agrometeorological and air pollution monitoring, to assess whether local ozone concentrations were capable of inducing damage to vegetation growing under northern Fennoscandia conditions. In 2018, we indeed observed ozone damage on clover and tobacco. In contrast, no such damage was found on the clovers in 2019. This indicates that key environmental variables in 2018 differed from 2019.

>>>>

We estimated the biomass reductions in accordance to the CLs \citep{ICP:MappingManual2017, ESPR:Hayes2021} for the most extreme temperature parameterization localization (\emph{subarctic}) for each PFT. The estimates for SWP=off are listed in Table~\ref{tab:biomass_reduction}. We defined an uncertainty range from the difference in biomass reduction caused by the variation of $f_\mathrm{light}$. Superscript refers to PPFD0.8 and subscript to PPFD1.2. The reported range corresponds to the effect of taking SWP into account or not. As SWP reduces $\mathrm{POD_1}$, biomass reduction is decreased when taking SWP into account. The biomass reduction ranges between $2.5\,\unit{\%}$ (coniferous, 2018) and $17.4\,\unit{\%}$ (deciduous, 2019). For deciduous trees this amounts to a reduction by up to $55\,\unit{\%}$ compared to MM.
Coniferous trees are the least affected PFT and the magnitude of total biomass reduction is almost independent of the choice of the parameterization within given uncertainties.

@@

@@

We found that 2018 was warmer, drier, and brighter than usual, while 2019 was a rather average year. Ozone was more enhanced in 2018 than 2019 due to large forest fires in Central Sweden. We derived localized temperature and light response functions for modeling $\mathrm{POD_1}$ and biomass reduction using the $\mathrm{DO_3SE}$ model and found that vegetation that is sensitive to warm temperatures could be less effected by ozone stress under heat stress conditions. On the other hand, vegetation that thrives better in a warmer climate could be more effected by coincident elevated $\chi_{O_3}$.

The qualitative bio-monitoring study which we conducted at Svanhovd along conventional ozone monitoring showed more visible ozone damage on clover and tobacco in 2018. In contrast, no such damage was found on the clovers in 2019. However, visible damage is not necessarily related to the modeled reductions in biomass.

Our study shows that it could be essential for ozone risk assessments in the subarctic to take the proper plant physiology into account as the difference in biomass reduction compared to the usually used parameterizations could amount to $55\,\unit{\%}$ (deciduous trees). We found an above ground biomass reductuion in perennial grassland of well above $10\,\unit{\%}$. From an agro-economical point of view in our focus area, where the grass is cut only once a year, a loss of biomass of more than $10\,\unit{\%}$ can have severer consequences compared to more productive areas in central Europe. Therefore, CL may also need localization.

@@
